### 2018-03-19 submission/manuscript.tex
update title

\section{Making Sense of the Noise: Leveraging Existing 16S rRNA Gene
Surveys to Identify Key Community Members in Colorectal
Tumors}\label{making-sense-of-the-noise-leveraging-existing-16s-rrna-gene-surveys-to-identify-key-community-members-in-colorectal-tumors}

>>>>

\section{Leveraging Existing 16S rRNA Gene Surveys to Identify
Reproducible Biomarkers in Individuals with Colorectal
Tumors}\label{leveraging-existing-16s-rrna-gene-surveys-to-identify-reproducible-biomarkers-in-individuals-with-colorectal-tumors}

### 2018-03-19 submission/supplemental.Rmd
Fix Table S4 formatting issues
update title

# Making Sense of the Noise: Leveraging Existing 16S rRNA Gene Surveys to Identify Key Community Members in Colorectal Tumors

@@

@@

\blandscape

@@

kable(combined_table_S5, format = "markdown", align = 'c', padding = 2)

@@

\elandscape
\newpage

>>>>

# Leveraging Existing 16S rRNA Gene Surveys to Identify Reproducible Biomarkers in Individuals with Colorectal Tumors

@@

\scriptsize

@@

@@

kable(combined_table_S5, format = "markdown", align = 'c', padding = 0)

@@
